skater: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2021-09-07 paper/paper.Rmd
orcid IDs, remove comments

authors:
  - name: Stephen D. Turner
    orcid: 0000-0001-9140-9028
    affiliation: "1"
  - name: V.P. Nagraj
    orcid: 0000-0003-0060-566X
    affiliation: "1"
  - name: Matthew Scholz
    orcid: 0000-0003-3686-1227
    affiliation: "1"
  - name: Shakeel Jessa
    affiliation: "1"
  - name: Carlos Acevedo
    affiliation: "1"
  - name: Jianye Ge
    orcid: 0000-0001-8724-075X
    affiliation: "2,3"
  - name: August E. Woerner
    orcid: 0000-0002-9372-1127
    affiliation: "2,3"
  - name: Bruce Budowle
    orcid: 0000-0003-4116-2930
    affiliation: "2,3"

@@

<!-- # Acknowledgements {.unnumbered} -->

<!-- These should be included at the end of the text and not in footnotes. Please ensure you acknowledge all sources of funding, see funding section below. -->

<!-- Details of all funding sources for the work in question should be given in a separate section entitled 'Funding'. This should appear before the 'Acknowledgements' section. -->

@@

<!-- -   The sentence should begin: 'This work was supported by ...' - -->

<!-- -   The full official funding agency name should be given, i.e. 'National Institutes of Health', not 'NIH' (full RIN-approved list of UK funding agencies) -->

<!-- -   Grant numbers should be given in brackets as follows: '[grant number xxxx]' -->

<!-- -   Multiple grant numbers should be separated by a comma as follows: '[grant numbers xxxx, yyyy]' -->

<!-- -   Agencies should be separated by a semi-colon (plus 'and' before the last funding agency) -->

<!-- -   Where individuals need to be specified for certain sources of funding the following text should be added after the relevant agency or grant number 'to [author initials]'. -->

<!-- An example is given here: 'This work was supported by the National Institutes of Health [AA123456 to C.S., BB765432 to M.H.]; and the Alcohol & Education Research Council [hfygr667789].' -->

<!-- Oxford Journals will deposit all NIH-funded articles in PubMed Central. See Depositing articles in repositories -- information for authors for details. Authors must ensure that manuscripts are clearly indicated as NIH-funded using the guidelines above. -->

>>>>

authors:
  - name: Stephen D. Turner
    orcid: 0000-0001-9140-9028
    affiliation: "1"
  - name: V.P. Nagraj
    orcid: 0000-0003-0060-566X
    affiliation: "1"
  - name: Matthew Scholz
    orcid: 0000-0003-3686-1227
    affiliation: "1"
  - name: Shakeel Jessa
    orcid: 0000-0002-1953-6839
    affiliation: "1"
  - name: Carlos Acevedo
    orcid: 0000-0002-1953-6839
    affiliation: "1"
  - name: Jianye Ge
    orcid: 0000-0001-8724-075X
    affiliation: "2,3"
  - name: August E. Woerner
    orcid: 0000-0002-9372-1127
    affiliation: "2,3"
  - name: Bruce Budowle
    orcid: 0000-0003-4116-2930
    affiliation: "2,3"

@@

@@
